Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-02-27 ms.tex
blah
n

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), and velocity ({\it bottom}),
    calculated for a representative sample of galaxies.  Different colors
    denote different values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
    galaxies ($\Gamma$=0.8) and thick lines correspond to core
    galaxies ($\Gamma$=0.1). Squares mark the location of
    the stagnation radius for each solution {\bf BDM: added colored labels for the $v_w$ value, e.g. a blue 1200 km/s directly to the top figure.  what does v/cs look like?} .
 }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{bh_growth.eps}
\caption{\label{fig:bh_growth} Growth times $\Mdot/\MdotEdd$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, blue) and cusp
  ($\Gamma=0.8$, green). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (purple) from
  equation~\eqref{eq:tgrow_min}. {\bf BDM: add Compton and Ia heating lines!}}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), and velocity ({\it bottom}),
    calculated for a representative sample of galaxies.  Different colors
    denote different values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
    $\Mbh=10^8 \Msun$ ({\it dashed}). Thin lines correspond to cusp
    galaxies ($\Gamma$=0.8) and thick lines correspond to core
    galaxies ($\Gamma$=0.1). Squares mark the location of
    the stagnation radius for each solution
 }
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mdot_sfr.pdf}
\caption{\label{fig:bh_growth} {\it Bottom panel:} Growth times $\Mbh/\Mdot$ in units
  of the Hubble time $\th$ for core ($\Gamma=0.1$, solid black) and
  cusp galaxies ($\Gamma=0.8$, dash-dotted black). These are calculated from
  equation~\ref{eq:tgrow_analytic} with parameters chosen for the
  average star formation history at each $\Mbh$. We also plot a lower
  bound on growth time for a themally stable flow (yellow) from
  equation~\eqref{eq:tgrow_min}.}
\end{figure}
